An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/arch.tex
a comma
a little progress

We propose \app, an automatic verification framework for 
software configuration files.
In particular, \app can solve many sophisticated 
configuration errors (\eg, ordering errors, missing entry errors,
and fine-grained value correlation) that previous efforts cannot 
detect. As depicted in Figure~\ref{fig-overview}, 
a typical \app verification workflow has three steps:
translation, learning, and checking. In this section, we briefly
describe how does each step work.

@@

\para{Checking.}
The checker is used to detect rule violations in the configuration
files of interest. The inputs of the checker are the learned rules 
and the target configuration file to verify.
It outputs a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations, or a suspicious value.
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
\ennan{I really wanted to say we are using MaxSMT to check and rank
these errors ...}
In our experience, we find learned rules can be significantly reused
to check different configuration files, thus improving our usability.

>>>>

We propose \app, an automatic verification framework for 
software configuration files.
In particular, \app can solve many sophisticated 
configuration errors (\eg, ordering errors, missing entry errors,
and fine-grained value correlation errors) that previous efforts cannot 
detect. As depicted in Figure~\ref{fig-overview}, 
a typical \app verification workflow has three steps:
translation, learning, and checking. In this section, we briefly
describe how each step works.

@@

\para{Checking.}
The checker is used to detect rule violations in the configuration
files of interest. The inputs of the checker are the learned rules 
and the target configuration file to verify.
It outputs a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations or a suspicious value.
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
\ennan{I really wanted to say we are using MaxSMT to check and rank
these errors ...}
In our experience, we find learned rules can be significantly reused
to check different configuration files, thus improving our usability.
